\documentclass[letterpaper,11pt]{article}

%\usepackage{times}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[style=ieee,backend=biber,url=false]{biblatex}
\addbibresource{local.bib}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeTwoList}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Drew Ripberger} \\ \vspace{1pt}
    \small (513)-413-3443 $|$ \href{mailto:drew.ripberger@gmail.com}{\underline{drew.ripberger@gmail.com}} $|$ 
    \href{https://linkedin.com/in/drewrip}{\underline{linkedin.com/in/drewrip}} $|$
    \href{https://github.com/drewrip}{\underline{github.com/drewrip}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeTwoList
      {The Ohio State University}{Columbus, OH}
      {Bachelors of Science in Computer Science and Engineering; GPA: 3.92}{Aug. 2020 -- Expected Dec. 2023}
      {With Summa Cum Laude Honors}{}
  \resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{Awards}
  \resumeSubHeadingListStart
    \resumeTwoList
      {The Ohio State University Computer Science Department}{Columbus, OH}
      {Shan and Qian Shan Kuo Endowed Scholarship}{Award of \$2,000}
      {Undergraduate Research Award}{Award (1 of 2 recipients) of \$1,000}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      
    \resumeSubheading
      {Software Engineering Intern}{Mar. 2020 -- Aug. 2020}
      {Nirmata}{San Jose, CA (remote)}
      \resumeItemListStart
        \resumeItem{Worked to help develop observability solutions to supply data upstream to Nirmata's Kubernetes management dashboard}
        \resumeItem{Used Go, eBPF and the Kubernetes API to construct a DaemonSet that monitors a cluster's network}
        \resumeItem{Presented the project to the CEO, CTO and VP of Engineering and wrote the project's announcement blog post}
        \resumeItem{Spoke at KubeCon + CloudNativeCon North America 2020 about my work developing kube-netc and entering the Kubernetes space: ``A High-Schooler's Guide to Kubernetes Network Observability''}
      \resumeItemListEnd 

    \resumeSubheading
      {Summer Research Intern}{Apr. 2021 -- Aug. 2021}
      {HyperThought Group at Ohio State}{Columbus, OH (remote)}
      \resumeItemListStart
        \resumeItem{Created infrastructure for parsing and storing unstructured image metadata using Python}
        \resumeItem{Developed code to detect defects in metals from electron microscopy images using OpenCV}
        \resumeItem{Collaborated with the Air Force Research Labs to interface and upload images and metadata onto the HyperThought system for further analysis and identification}
        \resumeItem{Assisted in writing an extended abstract and talk for Microscopy \& MicroAnalysis 2021 on how HyperThought can help doing large scale analysis of microscopy data}
      \resumeItemListEnd

      \resumeSubheading
      {Undergraduate Research Intern}{Jun. 2022 -- Aug. 2022}
      {Microsoft Research}{Redmond, WA (remote)}
      \resumeItemListStart
        \resumeItem{Learned about zkSNARKs, proof systems, and other cryptographic primitives while being mentored by Dr. Srinath Setty}
        \resumeItem{Worked with Dr. Setty on demonstrating and understanding the efficacy of incremental SNARKs}
        \resumeItem{Created a provable end-to-end banking transaction processing library in Rust based on recently published Nova recursive SNARKs}
        \resumeItem{Wrote constraints to encode operations on merkle trees and signature verification into R1CS circuits}
      \resumeItemListEnd

      \resumeSubheading
      {Software Engineering Intern, Performance and Scale Team}{May 2023 -- Aug. 2023}
      {Red Hat}{Boston, MA (remote)}
      \resumeItemListStart
        \resumeItem{Worked on evaluating the Trimaran load-aware scheduler for use in Red Hat Open Data Science (RHODS)}
        \resumeItem{Designed large scale tests to evaluate the Trimaran scheduler under heavily load and in massive clusters}
        \resumeItem{Collaborated with the Performance and Scale Team and IBM Research to determine optimal use cases for the various scheduling strategies}
        \resumeItem{Used systems automation tools including Ansible and Python to coordinate reproducible and open source tests}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{kube-netc} $|$ \emph{Go, Docker, Prometheus, Kubernetes, eBPF, TravisCI}}{Mar. 2020 -- Aug. 2020}
          \resumeItemListStart
            \resumeItem{An open source network observability tool for tracking network statistics across Kubernetes clusters}
            \resumeItem{Utilized eBPF to pull raw networking data from Linux containers}
            \resumeItem{Created Go libraries to process and expose the networking data as Prometheus metrics}
            \resumeItem{Was the focus of my 6 month internship at Nirmata}
            \resumeItem{The source code may be found on the GitHub repository: https://github.com/nirmata/kube-netc}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Rust, C/C++, Java, \LaTeX, JavaScript, SQL, Python} \\
     \textbf{Tools \& Systems}{: Git, Docker, eBPF, Linux, Prometheus, Kubernetes} \\
    }}
 \end{itemize}

% -----------PUBLICATIONS-----------

\nocite{*}
\printbibliography[title=Publications]
 
%-------------------------------------------
\end{document}
